### 2011-09-08 paper.tex
TAG rules

@@

$\startsymbol$

>>>>

% Parse trees
\usepackage{qtree}

@@

\Tree[ .$\epsilon$ [ .$\startsymbol$ [ .$\epsilon$ ] ] ]

Each ``intermediate tree'' is, formally, an ordered tree whose nodes are labeled from
$(\nodelabels \cup \terminals^\ast)$.

The transformation rules can take the following forms:

\tiny
\begin{tabular}{m{.2in}m{1in}m{.2in}m{1in}}
(1) &
\Tree[ .$\alpha$ [ .$A$ [ .$\beta$ ] ] ]
 & $\to$ & 
\Tree[ .$\alpha$ [ .$B$ [ [ [ .$C$ $\epsilon$ ] ] [ [ .$\beta$ ] ] ] ] ]
\\ \hline
(2) &
\Tree[ .$\alpha$ [ .$A$ [ .$\beta$ ] ] ]
 & $\to$ & 
\Tree[ .$\alpha$ [ .$B$ [ [ [ .$\beta$ ] ] [ [ .$C$ $\epsilon$ ] ] ] ] ]
\\ \hline
(3) &
\Tree[ .$\alpha$ [ .$A$ [ .$\beta$ ] ] ]
 & $\to$ & 
\Tree[ .$\alpha$ [ [ [ .$C$ $\epsilon$ ] ] [ [ .$B$ $\beta$ ] ] ] ]
\\ \hline
(4) &
\Tree[ .$\alpha$ [ .$A$ [ .$\beta$ ] ] ]
 & $\to$ & 
\Tree[ .$\alpha$ [ [ [ .$B$ $\beta$ ] ] [ [ .$C$ $\epsilon$ ] ] ] ]
\\ \hline
(5) &
\Tree[ .$\alpha$ [ .$A$ [ .$\beta$ ] ] ]
 & $\to$ & 
\Tree[ .$\alpha$ [ .$B$ [ .$C$ $\beta$ ] ] ]
\\ \hline
(6) &
\Tree[ .$\alpha$ [ .$A$ [ .$\beta$ ] ] ]
 & $\to$ & 
\Tree[ .$\alpha$ [ $u$ [ .$B$ [ $v$ [ $\beta$ ] $w$ ] ] $x$ ] ]
\end{tabular}
\normalsize

Here $\alpha,\beta$ represent any subtree;
$A \in \nodelabels$ is the source node label;
$B,C \in (\nodelabels \cup \{\epsilon\})$ are the destination node labels;
and
$u,v,w,x \in \terminals^\ast$ are (possibly empty) terminal strings.
